Metric Spaces with Expensive Distances

### 2019-04-16 paper/expensive-distances-main.tex
interim

\begin{figure}[ht]
    \begin{centering}
\begin{tikzpicture}
    \begin{axis}[xlabel=\# Points,ylabel=\# Edges / \# Points,
        legend pos=outer north east]

@@

\end{axis}
\end{tikzpicture}
\end{centering}
    \caption{Ratio \# edges / \# points for different variants of spanner 
    algorithms. The plot is for normally distributed points
    in dimension 2, $\eps = 0.1$.}
    \label{fig:spanner_ratio}
\end{figure}

\begin{figure}[ht!]
    \includegraphics[width=0.7\textwidth]{\expDistFigPath blind-greedy-dims.png}
    \caption{Results of blind greedy spanner for different dimensions.}
    \label{fig:blind_greedy_dimensions}
\end{figure}

@@

\begin{figure}[ht!]
    \begin{centering}
\begin{tikzpicture}
    \begin{axis}[xlabel=epsilon,ylabel=\# Edges,
        legend pos=outer north east]

\end{axis}
\end{tikzpicture}
\end{centering}
    \caption{Number of edges in the blind greedy and greedy spanners for different values of $\eps$. Data is for 400 normally distributed points in $\RR^2$ and $\RR^3$.}
    \label{fig:spanner_eps_dependence}
\end{figure}

@@

\begin{table}[]
\begin{tabular}{|l|l|l|}
\hline
dimension & \textbf{Greedy (non-blind)} & \textbf{Blind greedy} \\ \hline
2         &         1.08                &  1.12                 \\ \hline
3         &         1.24                &  1.41                \\ \hline
4         &         1.42                &  1.77                 \\ \hline
\end{tabular}
\caption{Estimated exponents in the $|E|= C |V|^\alpha$ dependence of the number of edges
on the number of points. The data is for $\eps = 0.1$ and for uniform points.}
\label{tbl:regr_coeff_spanner}
\end{table}

@@

From these experiments we conclude that the algorithm with the highest chance
of saving a significant amount of distance computations on real data, like large
persistence diagrams, is \bgrdy. Even though \brdnm also substantially reduces
the number of computed distances, its performance is significantly worse;
other algorithms that we tested do not produce sparse spanners.
While it would seem plausible that access to approximate value of the distance 
could be exploited in the spanner construction, 
we could not find a working heuristic; \bqsgrdy and \bqsshaker produce extremely
dense spanners.

@@

\begin{figure}[ht]
    \includegraphics[width=0.7\textwidth]{\expDistFigPath log_dependency_constant_ratio.png}
    \caption{Ratio $\log(\mbox{computed distances}) / n$ for ANN algorithm. Data is for uniformly distributed
    points.}
    \label{fig:ann_const_ratio}
\end{figure}

\begin{figure}[ht]
    \includegraphics[width=0.7\textwidth]{\expDistFigPath ann_computed_distances_dimension_dep.png}
    \caption{Number of computed distances for different dimensions. Points are chosen uniformly, $\eps = 0.01$.}
    \label{fig:ann_dimension_dependence}
\end{figure}

>>>>

\begin{figure}
\captionsetup[subfigure]{font=footnotesize}
\centering
\subcaptionbox{Ratio \# edges / \# points for different variants of spanner 
            algorithms. The plot is for normally distributed points
            in dimension 2, $\eps = 0.1$.}[.5\textwidth]{%
\begin{tikzpicture}
    \begin{axis}[xlabel=\# Points,ylabel=\# Edges / \# Points,
        legend pos=north east]

@@

    \end{axis}
            \label{fig:spanner_ratio}
\end{tikzpicture}}%
\subcaptionbox{Number of edges in the blind greedy and greedy spanners for different values of $\eps$. Data is for 400 normally distributed points in $\RR^2$ and $\RR^3$.}[.5\textwidth]{
    \begin{tikzpicture}
            \begin{axis}[xlabel=epsilon,ylabel=\# Edges,
                legend pos=north east]

        \end{axis}
        \label{fig:spanner_eps_dependence}
    \end{tikzpicture}}
\end{figure}

%\begin{figure}[ht]
%    \begin{minipage}{0.45\textwidth}
%        \begin{tikzpicture}
%            \begin{axis}[xlabel=\# Points,ylabel=\# Edges / \# Points,
%                legend pos=north east]

%                \addplot+ table [x=n_points, y=ratio_blind_random_lower_bound_first, col sep=comma] {\expDistDataPath all_methods_dim_2_eps_0.1_ratio.csv};
%                \addlegendentry{Blind random, lower bound first}

%                \addplot+ table [x=n_points, y=ratio_blind_greedy, col sep=comma] {\expDistDataPath all_methods_dim_2_eps_0.1_ratio.csv};
%                \addlegendentry{Blind greedy}

%                \addplot+ table [x=n_points, y=ratio_greedy, col sep=comma] {\expDistDataPath all_methods_dim_2_eps_0.1_ratio.csv};
%                \addlegendentry{Greedy}

%            \end{axis}
%        \end{tikzpicture}
%            \caption{Ratio \# edges / \# points for different variants of spanner 
%            algorithms. The plot is for normally distributed points
%            in dimension 2, $\eps = 0.1$.}
%            \label{fig:spanner_ratio}
%    \end{minipage}
%    \begin{minipage}{0.45\textwidth}
%        \begin{tikzpicture}
%            \begin{axis}[xlabel=epsilon,ylabel=\# Edges,
%                legend pos=north east]

%            \addplot+ table [x=Epsilon, y=edges_greedy_dim_2, col sep=comma] {\expDistDataPath eps_dep.csv};
%            \addlegendentry{Greedy, dim = 2}

%            \addplot+ table [x=Epsilon, y=edges_blind_greedy_dim_2, col sep=comma] {\expDistDataPath eps_dep.csv};
%            \addlegendentry{Blind greedy, dim = 2}

%        \end{axis}
%        \end{tikzpicture}
%        \caption{Number of edges in the blind greedy and greedy spanners for different values of $\eps$. Data is for 400 normally distributed points in $\RR^2$ and $\RR^3$.}
%        \label{fig:spanner_eps_dependence}
%   \end{minipage}
%\end{figure}

@@

\begin{figure}[ht!]
    \begin{centering}
    \includegraphics[width=0.8\textwidth]{\expDistFigPath blind-greedy-dims.png}
    \caption{Results of \bgrdy spanner for different dimensions.}
    \label{fig:blind_greedy_dimensions}
    \end{centering}
\end{figure}

@@

\begin{table}[b]
\begin{tabular}{|l|l|l|}
\hline
dimension & \textbf{Greedy (non-blind)} & \textbf{Blind greedy} \\ \hline
2         &         1.08                &  1.12                 \\ \hline
3         &         1.24                &  1.41                \\ \hline
4         &         1.42                &  1.77                 \\ \hline
\end{tabular}
\caption{Estimated exponents in the $|E|= C |V|^\alpha$ dependence of the number of edges
on the number of points. The data is for $\eps = 0.1$ and for uniform points.}
\label{tbl:regr_coeff_spanner}
\end{table}

@@

From these experiments we conclude that the algorithm with the highest chance
of saving a significant amount of distance computations on real data, like large
persistence diagrams, is \bgrdy. Even though \brndm also substantially reduces
the number of computed distances, its performance is significantly worse;
other algorithms that we tested do not produce sparse spanners.
While it would seem plausible that access to approximate value of the distance 
could be exploited in the spanner construction, 
we could not find a working heuristic; \bqsgrdy and \bqsshaker produce extremely
dense spanners.

@@

\begin{figure}[ht]
    \begin{minipage}{0.45\textwidth}
        \includegraphics[width=0.9\textwidth]{\expDistFigPath log_dependency_constant_ratio.png}
        \caption{Ratio $\log(\mbox{computed distances}) / n$ for ANN algorithm. Data is for uniformly distributed
        points.}
        \label{fig:ann_const_ratio}
    \end{minipage}
    \begin{minipage}{0.45\textwidth}
        \includegraphics[width=0.9\textwidth]{\expDistFigPath ann_computed_distances_dimension_dep.png}
        \caption{Number of computed distances for different dimensions. Points are chosen uniformly, $\eps = 0.01$.}
        \label{fig:ann_dimension_dependence}
    \end{minipage}
\end{figure}
